The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-27 science_ms.tex
Added figure of halo mass fn and galaxy luminosities.
Added some details about the simulation.  Revised after another proofreading.  Removed a paragraph in the discussion.  Within 80 words of the word limit, including the acknowledgements.  I think this should be fine.

\author
{John H.~Wise,$^{1,2\ast}$ Michael L.~Norman,$^{3}$ Tom Abel$^{4}$,
Matthew J.~Turk$^{3}$\\
\\
\normalsize{$^{1}$Department of Astrophysical Sciences, Princeton
University,}\\
\normalsize{Peyton Hall, Ivy Lane, Princeton, NJ 08544}\\
\normalsize{$^{2}$Hubble Fellow}\\
\normalsize{$^{3}$Center for Astrophysics and Space Sciences,}\\
\normalsize{University of California at San Diego, La Jolla, CA 92093}\\
\normalsize{$^{4}$Kavli Institute for Particle Astrophysics and
  Cosmology, }\\
\normalsize{Stanford University, Menlo Park, CA 94025}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:
jwise@astro.princeton.edu}
}

@@

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \cite{ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A fraction of
these stars enrich the surrounding intergalactic medium (IGM) when
they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe (PISNe; \cite{2002ApJ...567..532H}).  The host
halo and the neighboring halos are then enriched with this ejecta.
There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
dust cooling is efficient \cite{Omukai05, Schneider06_Frag, clark08}
and $\sim 10^{-3.5} Z_\odot$ otherwise \cite{Bromm01,
  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
be occur if the gas cooling is suppressed to the cosmic microwave
background (CMB) temperature \cite{Larson98, Tumlinson07_IMF,
  2009ApJ...691..441S}.  The resulting Population II star cluster will
thus have a lower characteristic stellar mass than its metal-free
progenitors.  These first stellar clusters may be connected to stars
in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
both with a metallicity floor of [Z/H] = --4 \cite{Beers05,
  Tafelmeyer10, Frebel10_Obs}.

@@

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Report, we present the simulations that include both types of SF, and
their radiative and mechanical feedback.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  This is the first time it has been
possible to link the formation and feedback of the first stars to
protogalaxies resolving the important scales and including the most
important physical effects.

@@

Here we present the gaseous and stellar evolution of two selected
halos in the simulation: one that has an early mass buildup but no
major mergers after $z=12$, and one that experiences a series of major
mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
``intense'', respectively.

\textbf{Add some interesting stats about the simulation.}

@@

Figure \ref{fig:evo}a shows the total, metal-enriched stellar, and gas
mass history of the most massive progenitors of both halos.  The quiet
halo undergoes a series of major mergers at $z > 12$, growing by a
factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
only grows by a factor of 3 by $z=7$ mainly through smooth accretion
from the filaments and IGM.  It is the most massive halo in the
simulation between redshifts 13 and 10.  At the same time, the intense
halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained in a
biased region on a comoving scale of 50 kpc with $\sim25$ halos with
$M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically merge to
form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts 10
and 7.9, seen in the rapid increases in total mass in Figure
\ref{fig:evo}a.  The merger history of the two halos are not atypical
as dark matter halos can experience both quiescent and vigorous mass
accretion rates in their buildup.

Both halos start forming Pop II stars when $M = 10^7 \Ms$.  This is
consistent with the filtering mass $M_f$ of high-redshift halos when
it accretes mainly from a pre-heated IGM \cite{gnedin98, gnedin00,
  Wise08_Gal}.  Afterwards these halos can cool efficiently through
\hh~cooling, sustaining constant and sometimes bursty SF.  The latter
characteristics are equated with the definition of a galaxy.  The
quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial starburst
photo-evaporates the majority of its molecular clouds, in addition to
heating and ionizing the surrounding IGM out to a radius of 10--15 kpc
at $z=9$.  These respectively reduce the in-situ and external cold gas
supply that could feed future SF.

The gas fractions of both halos decrease from 0.15 to 0.08 by outflows
driven by ionization fronts and blastwaves in their initial
starbursts.  The quiet halo never recovers to the cosmic fraction
$\Omega_b/\Omega_M$ for the following reason.  The lack of major
mergers of halos above the filtering mass leads to a small gas
fraction because halos with $M < M_f$ are likely photo-evaporated,
hosting diffuse warm gas reservoirs instead of cold dense cores.
After $z=10$, the halo mainly accretes warm diffuse gas from the
filaments and IGM.  In contrast, the intense halo grows from major
mergers of halos with $M > M_f$.  The progenitor halos involved in the
major mergers are able to host molecular clouds and have, in general,
higher gas fractions.  Between $z=10$ and $z=8$, the gas fraction
increases from 0.07 to 0.12 until it jumps to 0.14 when a gas-rich
major merger occurs.  The stellar mass accordingly increases with the
ample supply of gas during this period.  The gas fraction then
decreases by 0.01 when galactic outflows are generated from the
starburst associated with this major merger.

@@

In the quiet halo, an equilbrium of $[\bar{Z}_2/H] \sim -2.5$ is
established between metal-rich outflows and metal-poor inflows.
Galactic outflows are directed in the polar directions of the gas
disk, keeping the adjacent filaments metal-poor.  These features and a
well-mixed ISM (cf.~\cite{Wise08_Gal, Greif10}) are apparent in the
metallicity projections in Figure \ref{fig:projections}.  The average
stellar metallicity is within 0.5 dex of $[\bar{Z}_2/H]$.

In the intense halos, the first few Pop II star clusters have $[Z/H]$
between --1 and --2 and dominate the average stellar metallicity at $z
> 8$.  Afterwards the metallicity increases by a factor of 30 to
$[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
Because this halo is located in a large-scale overdensity, most of the
ejecta falls back into the halo after reaching distances up to 20
comoving kpc, in turn keeping the halo gas metallicity high because
the inflows are relatively metal-rich themselves.  After the $z \sim
8$ starburst, the average stellar metallicity follows the average gas
metallicity within 0.1 dex.

@@

The most massive progenitor of the quiet halo interestingly never
hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
the most massive progenitor, and the dense core survives this event
and is enriched by this PISN, triggering the transition to Pop II SF.
Other progenitors host three Pop III stars, forming at $z = 15.4,
14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
these two PISNe and Pop II SF quench Pop III SF in this halo.

The progenitors of the intense halo host a total of 56 Pop III stars
with 21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$
halo at $z=19$.  Pop III stars form on a regular interval in the
halo's progenitors until $z=9$ when most of these halos enter the
metal-rich bubble surrounding the intense halo.  There are two stars
forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds were
enriched by external blastwaves that only partially enriched the dense
regions.  This falls into the metallicity range where fragmentation
could occur if dust cooling is efficient below \tento{-4} $Z_\odot$.
The most massive progenitors of the intense halo cease to form Pop III
stars at $z<12$ because of nearby or intrinsic PISNe.

@@

Figure \ref{fig:pops} shows the SF history (SFH) of both halos.  The
metallicity distribution, SF rates, and metallicity evolution and
spread at a given time can all be extracted from these data.

A nearby PISNe provides a metallicity floor of [Z/H] = --2.8 in the
quiet halo at which metallicity the first Pop II stars form.  The
stellar metallicity evolution exhibits what is expected from an
isolated system with the stellar feedback steadily enriching the ISM,
resulting in a correlation between stellar age and metallicity.  After
$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
previously discussed.  The SFR peaks at $z=10$ and decreases as the
cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger
occurs, and the gas inside the satellite halo is compressed,
triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
This halo infalls through a filament, where most of metal enrichment
in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
disk and filament.  The filament and thus this satellite halo remains
relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
of the total stellar mass.

In contrast with the quiet halo, the intense halo undergoes a few
mergers of halos with an established stellar population.  This creates
a superposition of age-metallicity tracks in the SFH, seen in the
complexity of Figure \ref{fig:pops}.  The first two Pop II stellar
clusters have an unexpectedly high metallicity [Z/H] $\sim$ --1, which
occurs when a PISN blastwave triggers SF in two neighboring halos.
Most of the early SF have [Z/H] = --2.5.  At $z=9$, the halo's virial
temperature reaches \tento{4} K.  This combined with a 10:1 merger
creates a starburst that quickly enriches the halo to [Z/H] = --1.5 by
$z=8$.  The halo continues to enrich itself with further SF until
$z=7$.  The spikes in the scatter plot correspond to SN triggered SF
in nearby molecular clouds that are enriched up to a factor of 10 with
respect to the ISM.  However their mass fraction are small compared to
the total stellar mass.  The starburst at $z=9$ creates a bimodal
metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
the metal-rich component mainly being created after the starburst.
Two systems with sizable stellar components merge into the halo at $z
\sim 8$, and their stellar populations are still discernible in the
metallicity-age plot, whose tracks are noted by dashed lines.  Stars
with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.

@@

We also find that the merger history plays an important role in
supplying gas into halos after its first epoch of SF.  Mergers of
halos below the filtering mass are inefficient in providing gas
whereas the opposite is true for merging halos above the filtering
mass.  
% Halos do not necessarily need $\tvir \ge 10^4$ K to form significant
% stellar populations; however SFRs dramatically increase, and thus
% metal enrichment, when this threshold is reached.  Halos with mostly
% gas-poor mergers or a quiet merger history result in a monotonic
% increase in metallicity with time.  SFHs become more complex with
% multiple metallicity-age tracks if the halo experiences mergers with
% other halos that have an established stellar population.  Furthermore
% SF that is triggered by blastwaves interacting with molecular clouds
% can have metallicities up to a factor of 10 higher than the main
% starburst.
Starbursts at $\tvir = 10^4$ K can enrich the host halo enough to
create a bimodal metallicity distribution, where the metal-poor
component is created before the burst.  Note that mergers of stellar
populations can also create a similar bimodal distribution.  Such
distributions are observed in dSphs \cite{Battaglia10}.

We have shown that it is possible to simulate the formation of a
high-redshift dwarf galaxy and its entire SFH with radiative and
mechanical feedback.  This provides invaluable insight on the first
galaxies and the role of metal-free stars in the early universe.
There exists a wealth of information in this simulation, and we plan
to follow up this preliminary report with more detailed analysis of
the metal enrichment of the IGM, global SF rates, and observational
connections with high-redshift galaxies and Local Group dwarf galaxies
in the near future.

@@

>>>>

\author
{John H.~Wise,$^{1,2\ast}$ Matthew J.~Turk$^{3}$, Michael
  L.~Norman,$^{3}$ Tom Abel$^{4}$\\
\\
\normalsize{$^{1}$Department of Astrophysical Sciences, Princeton
University,}\\
\normalsize{Peyton Hall, Ivy Lane, Princeton, NJ 08544}\\
\normalsize{$^{2}$Hubble Fellow}\\
\normalsize{$^{3}$Center for Astrophysics and Space Sciences,}\\
\normalsize{University of California at San Diego, La Jolla, CA 92093}\\
\normalsize{$^{4}$Kavli Institute for Particle Astrophysics and
  Cosmology, }\\
\normalsize{Stanford University, Menlo Park, CA 94025}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:
jwise@astro.princeton.edu}
}

@@

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \cite{ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A fraction of
these stars enrich the surrounding intergalactic medium (IGM) when
they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe (PISNe; \cite{2002ApJ...567..532H}).  The host
halo and the neighboring halos are then enriched with this ejecta.
There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
dust cooling is efficient \cite{Omukai05, Schneider06_Frag, clark08}
and $\sim 10^{-3.5} Z_\odot$ otherwise \cite{Bromm01,
  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
be occur if the gas cooling is suppressed to the cosmic microwave
background (CMB) temperature \cite{Larson98, Tumlinson07_IMF,
  2009ApJ...691..441S}.  The resulting Population II star cluster will
thus have a lower characteristic stellar mass than its metal-free
progenitors.  These first stellar clusters may be connected to stars
in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
both with a metallicity floor of [Z/H]\footnote{We use the
  conventional notation, [Z/H] $\equiv$ log(Z/H) -
  log(Z$_\odot$/H$_\odot$)} = --4 \cite{Beers05, Tafelmeyer10,
  Frebel10_Obs}.

@@

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Report, we present the simulations that include both types of SF, and
their radiative and mechanical feedback.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  This is the first time it has been
possible to link the formation and feedback of the first stars to
protogalaxies, resolving the important scales and including the most
important physical effects.

@@

Here we present the gaseous and stellar evolution of two selected
halos in the simulation: one that has an early mass buildup but no
major mergers after $z=12$, and one that experiences a series of major
mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
``intense'', respectively.  The entire simulation contains 38 galaxies
with 3640 Pop II stellar clusters and captures the formation of 333
Pop III stars.  The halo mass function and galaxy luminosities are
plotted in Figure \ref{fig:massfn}.  This simulation has $1.4 \times
10^8$ computational elements and a maximal spatial resolution of 0.1
pc.

@@

Figure \ref{fig:evo}a shows the total, metal-enriched stellar, and gas
mass history of the most massive progenitors of both halos.  The quiet
halo undergoes a series of major mergers at $z > 12$, growing by a
factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
only grows by a factor of 3 by $z=7$ mainly through smooth accretion
from the filaments and IGM.  It is the most massive halo in the
simulation between redshifts 13 and 10.  At the same time, the intense
halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained in a
biased region on a comoving scale of 50 kpc with $\sim25$ halos with
$M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically merge to
form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts 10
and 7.9, seen in the rapid increases in total mass in Figure
\ref{fig:evo}a.  The merger history of the two halos are not atypical
as dark matter halos can experience both quiescent and vigorous mass
accretion rates.

Both halos start forming Pop II stars when $M = 10^7 \Ms$.  This is
consistent with the filtering mass $M_f$ of high-redshift halos when
it accretes mainly from a pre-heated IGM \cite{gnedin98, gnedin00,
  Wise08_Gal}.  Afterwards these halos can cool efficiently through
\hh~cooling, sustaining constant and sometimes bursting SF.  The
latter characteristics are equated with the definition of a galaxy.
The quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial
starburst photo-evaporates the majority of its molecular clouds, in
addition to heating and ionizing the surrounding IGM out to a radius
of 10--15 kpc at $z=9$.  These respectively reduce the in-situ and
external cold gas supply that could feed future SF.

The gas fractions of both halos decrease from 0.15 to 0.08 by outflows
driven by ionization fronts and blastwaves in their initial
starbursts.  The quiet halo never recovers to the cosmic fraction
$\Omega_b/\Omega_M$ for the following reason.  The lack of major
mergers of halos above the filtering mass leads to a small gas
fraction because halos with $M < M_f$ are likely photo-evaporated,
hosting diffuse warm gas reservoirs instead of cold dense cores.
After $z=10$, the halo mainly accretes warm diffuse gas from the
filaments and IGM.  In contrast, the intense halo grows from major
mergers of halos with $M > M_f$.  The progenitor halos involved in the
major mergers are able to host molecular clouds and have higher gas
fractions.  Between $z=10$ and $z=8$, the gas fraction increases from
0.07 to 0.12 until it jumps to 0.14 when a gas-rich major merger
occurs.  The stellar mass accordingly increases with the ample supply
of gas during this period.  The gas fraction then decreases by 0.01
when galactic outflows are generated from the starburst associated
with this major merger.

@@

In the quiet halo, an equilibrium of $[\bar{Z}_2/H] \sim -2.5$ is
established between metal-rich outflows and metal-poor inflows.
Galactic outflows are directed in the polar directions of the gas
disk, keeping the adjacent filaments metal-poor.  These features and a
well-mixed ISM (cf.~\cite{Wise08_Gal, Greif10}) are apparent in the
metallicity projections in Figure \ref{fig:projections}.  The average
stellar metallicity is within 0.5 dex of $[\bar{Z}_2/H]$.

In the intense halo, the first few Pop II star clusters have $[Z/H]$
between --1 and --2 and dominate the average stellar metallicity at $z
> 8$.  Afterwards the metallicity increases by a factor of 30 to
$[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
Because this halo is located in a large-scale overdensity, most of the
ejecta falls back into the halo after reaching distances up to 20
comoving kpc, keeping the halo gas metallicity high because the
inflows are relatively metal-rich themselves.  After the $z \sim 8$
starburst, the average stellar metallicity follows the average gas
metallicity within 0.1 dex.

@@

The most massive progenitor of the quiet halo interestingly never
hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
the most massive progenitor, and the dense core survives this event
and is enriched by this PISN, triggering the transition to Pop II SF.
Other progenitors host three Pop III stars, forming at $z = 15.4,
14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
these two PISNe and Pop II SF quench Pop III SF in this halo.  The
progenitors of the intense halo host a total of 56 Pop III stars with
21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$ halo at
$z=19$.  Pop III stars form on a regular interval in the halo's
progenitors until $z=9$ when most of these halos enter the metal-rich
bubble surrounding the intense halo.

% There are two stars forming at $z=7.7$ with [Z/H] = --5.7, whose
% molecular clouds were enriched by external blastwaves that only
% partially enriched the dense regions.  This falls into the metallicity
% range where fragmentation could occur if dust cooling is efficient
% below \tento{-4} $Z_\odot$.  The most massive progenitors of the
% intense halo cease to form Pop III stars at $z<12$ because of nearby
% or intrinsic PISNe.

@@

Figure \ref{fig:pops} shows the SF history (SFH), metallicity
distribution, and SF rates of both halos.  A nearby PISNe provides a
metallicity floor of [Z/H] = --2.8 in the quiet halo at which
metallicity the first Pop II stars form.  The stellar metallicity
evolution exhibits what is expected from an isolated system with the
stellar feedback steadily enriching the ISM, resulting in a
correlation between stellar age and metallicity.  After $z=10$ the
metallicities plateau at [Z/H] = --2.1 for reasons previously
discussed.  The SFR peaks at $z=10$ and decreases as the cold gas
reservoir is depleted.  Around $z=7.5$, a 25:1 minor merger occurs,
and the gas inside the satellite halo is compressed, triggering
metal-poor, [Z/H] = --3.2, SF during its nearest approach.  This halo
remains metal-poor because most of metal enrichment in the quiet halo
occurs in bi-polar flows perpendicular to the galaxy disk and
filament.  Stars with [Z/H] $<$ --3 compose 1.6 percent of the total
stellar mass.

In contrast with the quiet halo, the intense halo undergoes a few
mergers of halos with an established stellar population.  This creates
a superposition of age-metallicity tracks in the SFH, seen in the
complexity of Figure \ref{fig:pops}.  The first two Pop II stellar
clusters have an unexpectedly high metallicity [Z/H] $\sim$ --1, which
occurs when a PISN blastwave triggers SF in two neighboring halos.
Most of the early SF have [Z/H] = --2.5.  At $z=9$, the halo's virial
temperature reaches \tento{4} K.  This combined with a 10:1 merger
creates a starburst that quickly enriches the halo to [Z/H] = --1.5 by
$z=8$.  The halo continues to enrich itself afterwards.  The spikes in
the scatter plot correspond to SN triggered SF in nearby molecular
clouds that are enriched up to a factor of 10 with respect to the ISM.
However their mass fraction are small compared to the total stellar
mass.  The starburst at $z=9$ creates a bimodal metallicity
distribution with peaks at [Z/H] = --2.4 and --1.2 with the metal-rich
component mainly being created after the starburst.  Two systems with
sizable stellar components merge into the halo at $z \sim 8$, and
their stellar populations are still discernible in the metallicity-age
plot.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the total
stellar mass.

@@

% We also find that the merger history plays an important role in
% supplying gas into halos after its first epoch of SF.  Mergers of
% halos below the filtering mass are inefficient in providing gas
% whereas the opposite is true for merging halos above the filtering
% mass.  Halos do not necessarily need $\tvir \ge 10^4$ K to form
% significant stellar populations; however SFRs dramatically increase,
% and thus metal enrichment, when this threshold is reached.  Halos
% with mostly gas-poor mergers or a quiet merger history result in a
% monotonic increase in metallicity with time.  SFHs become more
% complex with multiple metallicity-age tracks if the halo experiences
% mergers with other halos that have an established stellar
% population.  Furthermore SF that is triggered by blastwaves
% interacting with molecular clouds can have metallicities up to a
% factor of 10 higher than the main starburst.  Starbursts at $\tvir =
% 10^4$ K can enrich the host halo enough to create a bimodal
% metallicity distribution, where the metal-poor component is created
% before the burst.  Note that mergers of stellar populations can also
% create a similar bimodal distribution, which are observed in dSphs
% \cite{Battaglia10}.

We have shown that it is possible to simulate the formation of a
high-redshift dwarf galaxy and its entire SFH with radiative and
mechanical feedback.  These results provide invaluable insight on the
first galaxies and the role of metal-free stars in the early universe.
There exists a wealth of information in this simulation, and we plan
to follow up this preliminary report with more detailed analysis of
the metal enrichment of the IGM, global SF rates, and observational
connections with high-redshift galaxies and Local Group dwarf galaxies
in the near future.

@@

\clearpage
\begin{figure*}
\includegraphics[width=0.6\textwidth]{Lstar.eps}
\caption{\label{fig:massfn} \textbf{Top}: Halo mass function of the
  simulation compared with the analytical fit (solid) of
  \cite{Warren06}.  \textbf{Bottom}: Total Pop II luminosities of
  halos with constant mass-to-light ratios overplotted.}
\end{figure*}
